Malacology: A Programmable Storage System

### 2016-10-12 paper/paper.tex
paper: fix graphs in mantle evaluation - touch up throughput graph - decided to leave the CPU graph because it shows no multi-threaded - fixed axes on both graphs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] A
ZLog sequencer that uses the Malacology load balancing interface enjoys the
load balancing features of the of the metadata cluster. The ``Sequencer
Baseline'' has no background sequencers, while the rest of the curves show the
throughput of 1 sequencer when an additional sequencer is running in the
background generating load.}\label{fig:mantle-seq-thruput}
\end{figure}

@@

We evaluate the load balancing interface by showing the performance
implications of shedding load. The experiments use our internal cluster which
uses 10 nodes to store objects, one node to monitor the cluster, and 3 nodes
that can accomodate sequencers. The workload is two logs, one with 7 clients
and the other with 8 clients; we chose this workload because this load is the
point at which a single physical server gets overloaded.

We use a balancer policy specifically designed for multiple sequencers. The
balancer aggressively sheds half its load to its neighbor as soon as it can.
It is based off the ``Greedy Spill Even" approach in the
Mantle~\cite{sevilla:sc15-mantle} paper but is reproduced in
Figure~\ref{listing:greedy-spill} for the reader's convenience.

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-cpu-utilization-annotate.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
sequencer using Mantle in Figure~\ref{fig:mantle-seq-thruput} migrates to a new
server immediately because it uses a policy designed for bursty workloads. This
is a trace of the same workload running twice: once with a single host server and once
with Mantle.}
\label{fig:mantle-cpu-utilization}
\end{figure}

Figure~\ref{fig:mantle-seq-thruput} shows a performance profile of one of the
sequencers as the load balancing interface migrates sequencers around the
cluster to alleviate load.  Each curve shows the throughput (\(y\) axis) over
time (\(x\) axis).  ``Sequencer Baseline'' is the performance of one sequencer
on one physical server serving 7 clients - there are no other sequencers or
logs in the system and the curve represents the maximum throughput of a
sequencer on an underutilized physical server.  ``No Load Balancing" adds a
second sequencer of equal load to the same physical server with the intent of
overloading the single physical server; recall that the throughput for this
second sequencer is omitted. Compared to the baseline, the overloaded physical
server with 2 sequencers has more than a 2\(\times\) throughput degradation.

The last two curves of Figure~\ref{fig:mantle-seq-thruput} show the performance
improvements when sequencers are load balanced across the cluster. Both curves
are the throughput of one of the sequencers when a background sequencer is
running. These policies differ by the threshold at which they start balancing:
``Sequencer Balancing Policy" starts balancing immediately and ``Conservative
Balancing Policy" waits for 120 seconds before migrating sequencers.

The variation of the sequencer throughputs helps us determine which sequencers
are on overloaded physical servers.  ``Sequencer Baseline" is the best
performance for this particular workload because there is no contention.
Performance is stable and the MDS is under-loaded because we do not see the
spike at the end like the other curves.  ``No Load Balancing" shows an
overloaded sequencer because the performance of the monitored sequencer is low
and unstable (high variation in performance). We also deduce that it is
overloaded by comparing to the ``Sequencer Balancing Policy" and ``Conservative
Balancing Policy" curves, which show improved performance when load is
migrated.

@@

Figure~\ref{fig:mantle-cpu-utilization} gives a time series graph to show the
behavior of the same workload, 2 sequencers, with balancing turned on and off.
The curves are the throughput (\(y\) axis) over time (\(x\) axis) and the graph
has been partitioned into the two cluster setup stages. The CPU utilization is
confined to one core because load balancer interface is not multi-threaded.
Recall the the load balancing interface re-uses the POSIX metadata cluster
migration mechanisms and as it has been shown that metadata performance does
not improve with multiple threads~\cite{konstantinos:pdsw2014-lustre-metadata}.

>>>>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
Performance profiles of a single sequencer running in a resource constrained
environment show the benefits of using the load balancing interface.  ``1
Sequencer Baseline'' is the throughput of one sequencer on an underloaded
physical server; the other curves show how load balancing affects the
throughput of one sequencer when sequencers for other logs are co-located on
the same physical server.}\label{fig:mantle-seq-thruput}
\end{figure}

@@

We evaluate the load balancing interface by showing how the cluster of servers
housing sequencers alleviate load.  The experiments use our internal cluster
which uses 10 nodes to store objects, one node to monitor the cluster, and 3
nodes that can accomodate sequencers. The workload is two logs, one with 7
clients and the other with 8 clients; we chose this workload because this load
is the point at which a single physical server gets overloaded.

We use a balancer policy specifically designed for multiple sequencers. The
balancer aggressively sheds half its load to the next server as soon as it can.
It is based off the ``Greedy Spill Even" approach in the
Mantle~\cite{sevilla:sc15-mantle} paper but is reproduced in
Figure~\ref{listing:greedy-spill} for the reader's convenience. An MDS is a
physical server capable of housing a sequencer.

@@

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-cpu-utilization.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
CPU utilization for a sequencer in an environment with the ``Conservative
Policy" load balancer shows that the load balancing service is not
multi-threaded. The load balancing service is designed this way because the
performance for a guarded resource will not improve with more cores.}
\label{fig:mantle-cpu-utilization}
\end{figure}

Figure~\ref{fig:mantle-seq-thruput} shows a performance profile of one of the
sequencers as the load balancing interface migrates sequencers around the
cluster to alleviate load.  Each curve shows the throughput (\(y\) axis) over
time (\(x\) axis).  ``1 Sequencer Baseline'' is the performance of one sequencer
on one physical server serving 7 clients - there are no other sequencers or
logs in the system and the curve represents the maximum throughput of a
sequencer on an underutilized physical server.  ``No Balancing" adds a
second sequencer of equal load to the same physical server with the intent of
overloading the single physical server; recall that the throughput for this
second sequencer is omitted. Compared to the baseline, the overloaded physical
server with 2 sequencers has more than a 2\(\times\) throughput degradation.
The stability of throughput curves (i.e. the variation on the \(y\) axis) indicate which sequencers
are on overloaded physical servers.  ``1 Sequencer Baseline" is the best
performance for this particular workload because there is no contention.
Performance is stable and the MDS is under-loaded because we do not see the
spike at the end like the other curves.  ``No Balancing" shows an
overloaded sequencer because the performance of the monitored sequencer is low
and unstable (high variation in performance).

The last two curves of Figure~\ref{fig:mantle-seq-thruput} show the performance
improvements when sequencers are load balanced across the cluster. Both curves
show the throughput of one of the sequencers when a second sequencer is
running on the same physical server. The load balancing policies differ by the threshold at which they start balancing:
``Sequencer Policy" starts balancing immediately and ``Conservative
Policy" waits for 120 seconds before migrating sequencers.

@@

Figure~\ref{fig:mantle-cpu-utilization} shows how load balancing effects the
physical servers by plotting the CPU utilization average over 1 minute (\(y\)
axis) over time (\(x\) axis).  It shows the ``Conservative Policy" load
balancer from the run in Figure~\ref{fig:mantle-seq-thruput}, so recall that
resources are constrained during the job by co-locating a second sequencer on
the same physical server.  CPU utilization spikes when physical servers receive
load (at 2 minutes physical server 1 receives a sequencer from physical server
0) but the CPU utilization never eclipses 50\%. The utilization is low because
the load balancer interface is not multi-threaded.  Recall the the load
balancing interface re-uses the POSIX metadata cluster migration mechanisms;
serving file system metadata is single-threaded because it has been shown that
metadata performance does not improve with multiple
threads~\cite{konstantinos:pdsw2014-lustre-metadata}.
